Switchboard and BNC Suprisal

### 2019-05-09 surprisal/bnc&switchboard.Rmd
worked out bootstrap for unigram surprisals

switch_surprisals <- switchboard %>%
  left_join(switch_unigrams) %>%
  mutate(s = -log(p)) %>%
  group_by(length, word_order) %>% 
  summarise(s = mean(s))
  # tidyboot_mean(s)

switch_surprisals %>%
  filter(length %in% c(3, 5, 7)) %>%
  ggplot(aes(x = word_order, y = s)) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_smooth(se = F)
```

```{r bootstrapping}

# extract_stem_tokens <- function(role, target_length, utterances) {
#   
#   if (role == "child") {
#     sub_utterances <- utterances %>%
#       filter(speaker_role == "Target_Child") %>%
#       mutate(length = str_count(stem, pattern = " +") + 1)
# 
# } else {
#     sub_utterances <- utterances %>%
#       filter(speaker_role != "Target_Child") %>%
#       mutate(length = str_count(stem, pattern = " +") + 1)
# }
#   
#   tokens <- sub_utterances %>%
#     filter(length == target_length) %>%
#     mutate(utterance_id = 1:n()) %>%
#     unnest_tokens(word, stem) %>%
#     group_by(utterance_id) %>%
#     mutate(word_order = 1:n()) %>%
#     group_by(word_order, word) %>%
#     filter(word_order <= length)
#    
  # tokens %>%
  #   summarise(n = n()) %>%
  #   tidyboot(summary_function = function(x) x %>%
  #              summarise(entropy = entropy(n, unit = "log2")),
  #            statistics_functions = function(x) x %>%
  #            summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
  #   mutate(role = role, length = target_length)
# }
```

@@

bnc_surprisals <- bnc %>%
  left_join(bnc_unigrams) %>%
  mutate(s = -log(p)) %>%
  group_by(length, word_order) %>%
  summarise(s = mean(s))

bnc_surprisals %>%
  ggplot(aes(x = word_order, y = s)) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_smooth(se = F)
```

>>>>

sw <- switchboard %>%
  left_join(switch_unigrams) %>%
  mutate(s = -log(p)) %>%
  ungroup() %>%
  select(length, word_order, s) %>%
  nest(s)

swc <- sw %>% filter(length %in% c(10, 20, 30))
switch_surprisals <- map_dfr(1:nrow(swc), 
        ~bind_cols(select(slice(swc, .x), length, word_order), 
                               tidyboot_mean(data = unnest(slice(swc, .x)), 
                                             column = s, nboot = 100)))

# switch_surprisals <- switchboard %>%
#   left_join(switch_unigrams) %>%
#   mutate(s = -log(p)) %>%
#   ungroup() %>%
#   select(length, word_order, s) %>%
#   filter(length %in% c(10, 20, 30)) %>%
#   group_by(length, word_order) %>% 
#   tidyboot_mean(s)

switch_surprisals %>%
  ggplot(aes(x = word_order, y = empirical_stat, #observed mean surprisal
             ymin = ci_lower, ymax = ci_upper)) + 
  facet_wrap(~ length) + 
  ylab("Surprisal") + 
  xlab("Word Position in Switchboard") + 
  geom_pointrange(size = .50) + 
  geom_line(size = .50)
```

@@

bnc_surprisals_prep <- bnc %>% 
  left_join(bnc_unigrams) %>%
  mutate(s = -log(p)) %>%
  ungroup() %>%
  select(length, word_order, s) %>%
  nest(s)

bnc_surprisals <- map_dfr(1:nrow(bnc_surprisals_prep), 
        ~bind_cols(select(slice(bnc_surprisals_prep, .x), length, word_order), 
                               tidyboot_mean(data = unnest(slice(bnc_surprisals_prep, .x)), 
                                             column = s, nboot = 100)))

# bnc_surprisals <- bnc %>%
#   left_join(bnc_unigrams) %>%
#   mutate(s = -log(p)) %>%
#   select(length, word_order, s) %>%
#   filter(length == 10) %>%
#   group_by(length, word_order) %>%
#   # summarise(s = mean(s)) 
#   tidyboot_mean(s)

bnc_surprisals %>%
  ggplot(aes(x = word_order, y = empirical_stat, #observed mean surprisal
             ymin = ci_lower, ymax = ci_upper)) + 
  facet_wrap(~ length) + 
  ylab("Surprisal") + 
  xlab("Word Position in BNC") + 
  geom_pointrange(size = .50) + 
  geom_line(size = .50)

# bnc_surprisals %>%
#   ggplot(aes(x = word_order, y = s)) + 
#   facet_wrap(~ length) + 
#   geom_point() + 
#   geom_smooth(se = F)
```
